%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Post-Graduate Internship in Software Development department} % Job title
    {\href{https://www.alpinformatica.com/}{Alpinformatica}} % Organization
    {Malè, TN 38020, Italy} % Location
    {Jan. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mobile Development: Flutter framework, built and managed the application ``Collegio Maestri di Sci Trentino''}
        \item {Development of management platforms thorough PHP and JQuery}
        \item {AWS Certified Cloud Practitioner, AWS Solution Architect}
        \item {Research and usage of different Design Patterns}
      \end{cvitems}
      }
%---------------------------------------------------------
  \cventry
    {Internship in Software Development department} % Job title
    {\href{https://www.alpinformatica.com/}{Alpinformatica}} % Organization
    {Malè, TN 38020, Italy} % Location
    {Aug. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of the thesis project, the voting system: Sedute Online}
        \item {SPID integration to mobile applications and SPID company accreditation}
      \end{cvitems}
      }
%---------------------------------------------------------
  \cventry
    {Internship in IT department} % Job title
    {\href{https://www.funiviecampiglio.it}{Funivie Madonna di Campiglio}} % Organization
    {Madonna di Campiglio, TN 38086, Italy} % Location
    {Jun. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web-app development, web-app testing, code refactoring, integration of BancaIntesa's API}
        \item {Optical fiber management, tech assistance, mobile Operative Systems compilation}
        \item {PHP 7, MySQL, Unicredit API, Android 5, Optical-fiber, GNU-Linux, FTP, Excel}
      \end{cvitems}
      }
    

%---------------------------------------------------------
  \cventry
    {Museum Guide} % Job title
    {\href{https://www.mmape.it}{MMape}} % Organization
    {Croviana, TN 38027, Italy} % Location
    {Apr. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Soft Skill developed:} public speaking, team-working and time-management}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Surveyor} % Job title
    {Studio Tecnico Fantelli} % Organization
    {Dimaro, TN 38025, Italy} % Location
    {Apr. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {CAD 2D, CAD 3D and Google Sketchup for blueprints developments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Civil Service - Educator and events organizer} % Job title
    {Progetto Giovani - APPM} % Organization
    {Dimaro, TN 38025, Italy} % Location
    {Jun. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Soft Skill developed:} problem-solving, communication and team-working.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
