%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {\href{www.reply.com/}{Reply, Cluster Clash IT}} % Organization
    {Milan, MI 20152, Italy} % Location
    {May 2023 - PRESENT} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generative AI: Prompt Engineering and development of Generative AI Solutions with Azure OpenAI API and SDK, Flask and React}
        \item {Microsoft Power Platform Solutions: Development and Deployment of Power Apps, Power Automate and Power BI solutions}
        \item {Backend: Python (Flask) and .NET (EF Core, Dapperer, ASP.NET) with SQL db interaction}
        \item {Frontend: React and Redux}
        \item {DevOps: Azure DevOps, Docker, Kubernetes, Azure Functions, Azure Logic Apps}
        \item {Scrum and Agile methodologies}
       \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.alpinformatica.com/}{Alpinformatica}} % Organization
    {Malè, TN 38020, Italy} % Location
    {Jan. 2022 - May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Main Mobile Developer: build, managment and deployment (Windows, iOS, Android and Huawei) of Flutter applications}
        \item {ERP and REST API development: PHP in LAMP environment on AWS resources}
        \item {AWS Serverless development: telegram bot, GPS analysis and computation, authentication services in Python and NodeJS}
        \item {Research and optimization of company DevOps Pipeline}
        \item {Internal utility tool development and research: personalized db migration tool, pdf modifier and various utility tools in Python}
        \item {SPID and CIE integration to mobile applications; SPID and CIE company accreditation}
        \item {\textbf{Soft Skill developed:} Functional communication}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Internship in Software Development department} % Job title
    {\href{https://www.alpinformatica.com/}{Alpinformatica}} % Organization
    {Malè, TN 38020, Italy} % Location
    {Aug. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of the thesis project, the voting system: Sedute Online}
        \item {SPID integration to mobile applications and SPID company accreditation}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
{Internship in IT department} % Job title
{\href{https://www.funiviecampiglio.it}{Funivie Madonna di Campiglio}} % Organization
{Madonna di Campiglio, TN 38086, Italy} % Location
{Jun. 2019 - Aug. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Web-app development for ticketing system, web-app testing, code refactoring, integration of BancaIntesa's API}
    \item {Optical fiber management, tech assistance, mobile Operative Systems compilation}
  \end{cvitems}
  }

  \cventry
{Part-time student work in IT department} % Job title
{\href{https://www.unitn.it}{University of Trento}} % Organization
{Trento, Italy} % Location
{2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Internal tool development}
  \end{cvitems}
  }

%---------------------------------------------------------
\cventry
{Tech Support} % Job title
{\href{https://www.mmape.it}{MMape}} % Organization
{Croviana, TN 38027, Italy} % Location
{Sep. 2016 - PRESENT} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Paypal API, Tech Support, Networking, Wordpress development and assistance}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Museum Guide} % Job title
{\href{https://www.mmape.it}{MMape}} % Organization
{Croviana, TN 38027, Italy} % Location
{Apr. 2016 - Sep. 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Soft Skill developed:} public speaking, team-working and time-management}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Surveyor} % Job title
{Studio Tecnico Fantelli} % Organization
{Dimaro, TN 38025, Italy} % Location
{Apr. 2016 - Sep. 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {CAD 2D, CAD 3D and Google Sketchup for blueprints developments.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Civil Service - Educator and events organizer} % Job title
{Progetto Giovani - APPM} % Organization
{Dimaro, TN 38025, Italy} % Location
{Jun. 2015 - Jun. 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Soft Skill developed:} problem-solving, communication and team-working.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
